---
title: "A UN Report on the Relationship between GDP and Life Expectancy and CO2"
author: "Evie"
date: "2023-01-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-packages}
library(tidyverse)
```

This report was prepared to the attention of the United Nations. It analyzes the relationship between a country's GDP, its life expectancy and CO2 emissions. Our goal is to determine to what degree a country’s economic strength or weakness may be related to its public health status and impact on climate pollution. We hypothesize that both life expectancy and CO2 emissions increase with a country's GDP.

```{r read-data}
gapminder_1997 <- read_csv("data/gapminder_1997.csv")
```


```{r gdp-lifeExp-1997-plot}
# make plot of GDP (x axis) vs LifeExp (y-axis)
ggplot(data=gapminder_1997)+
  aes(x = gdpPercap, y = lifeExp, color = continent, size=pop/1000000)+
  geom_point()+
  labs(x = "GDP Per Capita", y = "Life Expectancy (yrs)", size = "Population (in millions)")+
  scale_color_brewer(palette = "Set1")+
  theme_classic()
```

